Cloud Supercomputing

### 2019-04-25 writing/paper/paper.tex
added abstract. changed first sentences.

\begin{document}
\maketitle
\begin{abstract}

\begin{itemize}
\item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
\item Implementation in \exahypeengine{}, a scalable \pde{} framework.
\item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
\item Simulation of challenging flows over hydrostatic background atmosphere.
\item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
\end{itemize}

@@

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
This part requires both suitable physical models and effective computational realisations. 
We focus on the simulation of cloud formation processes with simple benchmark scenarios~\cite{giraldo2008study}.
These relatively small scale effects are well approximated with the compressible Navier-Stoks equations.
They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
It is well known that Runge-Kutta methods become more ineffecient for very high orders.
Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.

>>>>

\begin{document}
\maketitlet 
\begin{abstract}
  In the context of simulation of convective proceess for numerical weather prediction, we present an application of the compressible Navier Stokes equations on cloud formation processes.
  While established methods have to use tailored numerics towards the specific simulation, our generic scheme shows competitive results for both classical cfd and hydrostatic scenarios.
  Our scheme exploits an underlying parallelized implementation of the \aderdg{} method with dynamic adaptive mesh refinement. 
  We improve our method by a PDE independent general refinement criterion, based on the local total variation of the numerical solution.
  All together our method can be seen as a perfect candidate for large scale cloud simulation runs on current and future super computers.
\begin{itemize}
\item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
\item Implementation in \exahypeengine{}, a scalable \pde{} framework.
\item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
\item Simulation of challenging flows over hydrostatic background atmosphere.
\item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
\end{itemize}

@@

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
In this paper we address the resolution of convective processes in the context of numerical weather prediction (\textsc{nwp}), on modern super computer systems.
The simulation of these process, with suitable physical models and on large scale clusters is expected to play an important role in future \textsc{nwp}~\cite{bauer2015quiet}.
%% Numerical weather prediction (\textsc{nwp}) contains processes of different spatio-temporal scales.
%% An important part of future \textsc{nwp} models will be the the resolution of convective processes~\cite{bauer2015quiet}.
%% This part requires both suitable physical models and effective computational realisations. 
We focus on the simulation of cloud formation processes with simple benchmark scenarios~\cite{giraldo2008study}.
These relatively small scale effects are well approximated with the compressible Navier-Stokes equations.
The general approach is to use a space-discretized by higher order Galerkin method, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
%%They are often space-discretized by higher order Galerkin methods, as seen for example in~\cite{giraldo2008study,muller2010adaptive,muller2018strong}.
Even though all of these implementations use a discretization with a (theoretical) unlimited space-order, they use Runge-Kutta time integrators or semi-implicit methods.
It is well known that Runge-Kutta methods become more ineffecient for very high orders.
Furthermore, they and the implicit methods are more communication-intensive and thus require a larger overhead and are more complicated to scale.
